R Notebook

### 2021-06-21 Exemples and Implementations.Rmd
ho inserito examples e forecast

# Liu and West filter
# -------------------
set.seed(8642)
N      = 1000
```

@@

xs     = rnorm(N,m0,sqrt(C0))
pars   = cbind(rnorm(N,ealpha,sqrt(valpha)),rnorm(N,ebeta,sqrt(vbeta)),
               log(1/rgamma(N,nu/2,nu*lambda/2)))
delta  = 0.75
a      = (3*delta-1)/(2*delta)
h2     = 1-a^2
parss  = array(0,c(N,3,n))
xss    = NULL
ws     = NULL
ESS    = NULL
w      = rep(1/N,N)
for (t in 1:length(data)){
  mpar        = apply(pars,2,mean)
  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(data[t],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(y[t],0,exp(xt/2))/dnorm(y[t],0,exp(mus/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
N=1000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
#svlw<-SVLWfun(y,N=5000000,m0,C0,ealpha=0,valpha=1,ebeta=1,vbeta=1,nu=1,lambda=1)
```

```{r}
#Filtplot(dfsv,,"")
```

>>>>

# Liu and West filter
# -------------------
set.seed(8642)
N      = 10
```

@@

xs = rnorm(N,m0,sqrt(C0))
pars   = cbind(rnorm(N,ealpha,sqrt(valpha)),rnorm(N,ebeta,sqrt(vbeta)),
               log(1/rgamma(N,nu/2,nu*lambda/2)))
delta  = 0.75
a      = (3*delta-1)/(2*delta)
h2     = 1-a^2
parss  = array(0,c(N,3,n))
xss    = NULL
ws     = NULL
ESS    = NULL
w      = rep(1/N,N)
for (t in 1:length(data)){

  mpar        = apply(pars,2,mean)
  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(y[1],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(y[1],0,exp(xt/2))/dnorm(y[1],0,exp(mus[k]/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
N=1000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
svlw<-SVLWfun(y,N=1000,m0,C0,ealpha=0.12,valpha=0.4,ebeta=1,vbeta=0.3,nu=0.11,lambda=0.1)
```

```{r}
Filtplot(dfsv,svlw,"")
```
